\thetitle

### 2023-06-05 metatheory2.tex
Fix typo.

We review the base MLTT fragment of \TT first. The following rules are the fully expanded version of \cref{fig:mltt-selected}, where each type (except universes) has four kinds of rules: introduction, elimination, computation and uniqueness rules. Computation rules ($\beta$-rules) indicate the judgemental equality for expressing reduction when elimination rules apply to the introduction form. Uniqueness rules ($\eta$-rules) indicate how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.

@@

\TT extends the MLTT in \cref{sec:mltt-full} with W-type signatures and W-types,
linkage signatures and linkages, and linkage transformers. The following rules are the fully expanded version of \cref{fig:fmltt-selected}, where each type has five kinds of rules: introduction, elimination, computation, uniqueness rules and substitution lemma. 
Computation rules ($\beta$-rules) indicate the judgemental equality for expressing reduction when elimination rules apply to the introduction form. Uniqueness rules ($\eta$-rules) indicates how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.

>>>>

We review the base MLTT fragment of \TT first. The following rules are the fully expanded version of \cref{fig:mltt-selected}, where each type (except universes) has four kinds of rules: introduction, elimination, computation and uniqueness rules. Computation rules ($\beta$-equalities) indicate the judgemental equality for expressing reduction when elimination rules apply to the introduction form. Uniqueness rules ($\eta$-equalities) indicate how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.

@@

\TT extends the MLTT in \cref{sec:mltt-full} with W-type signatures and W-types,
linkage signatures and linkages, and linkage transformers. The following rules are the fully expanded version of \cref{fig:fmltt-selected}, where each type has five kinds of rules: introduction, elimination, computation, uniqueness rules and substitution lemma. 
Computation rules ($\beta$-equalities) indicate the judgemental equality for expressing reduction when elimination rules apply to the introduction form. Uniqueness rules ($\eta$-equalities) indicate how some terms are possibly uniquely constructed by introduction rules. The substitution rule is in the form of de Bruijn indices.
